Forecast of the 2024 Presidential Election through the Lens of Turbulent Battleground States

### 2024-11-04 paper/paper.qmd
Update paper.qmd
Final Paper Edit

## Target Population and Sampling Frame
The poll targets registered voters in the United States, with a particular focus on voters in swing states for presidential races. Consequently, the target population is registered voters of the United States of America and the sampling frame is the voter file, a national list of registered voters from which NYC employs random sampling to create their pollsters [@nyt_poll]. This voter file contains information on more than 200 million Americans that includes information about their party affiliation, voting history, and  basic demographic information. From this sampling frame, respondents are randomly selected while balancing key demographic and political characteristics through both front-end sampling and post-survey weighting pursuant to appropriate representation of the entire target population [@nyt_poll].

@@

## Non-Response Remedies
With a response rate of 2%, there is valid concern over non-response bias underrepresenting certain demographics. The poll addresses non-response through a combination of front-end sampling adjustments (calling harder-to-reach voters) and post-survey weighting. Weighting is applied to ensure that the final sample aligns with the demographic and political composition of the electorate, based on voter file data. Non-response bias is a persistent challenge, and even though weighting helps, it's impossible to be certain that respondents are fully representative of those who do not respond. Experiments with alternative methods, such as mail surveys with incentives of cash vouchers have shown to increase response rate up to 30% [@nyt_poll].

@@

The Times/Siena Poll’s approach to questionnaire design reflects a careful effort to craft unbiased, relevant, and inclusive questions. By tailoring questions to current events and topics of widespread interest, the poll aims to capture public sentiment on issues that directly affect voters' attitudes, such as economic conditions or recent political debates. This responsiveness to current events strengthens the poll's relevance and allows it to track shifts in opinion over time. The poll’s commitment to neutrality is a significant strength. Each question is designed to ensure that respondents, regardless of their political views, feel that their perspectives are fairly represented. The team behind the poll spends substantial time crafting response options to reflect a balanced spectrum of views, minimizing potential response bias and enhancing the questionnaire's reliability across different demographic and ideological groups [@nyt_poll]. Clarity is also a central focus in their questionnaire development. The team emphasizes ensuring that each question is clear and unambiguous, minimizing the risk of misinterpretation. This dedication to straightforward, widely understandable questions improves the validity of responses, as it reduces the chance that respondents interpret questions differently based on background or knowledge level.

@@

Although weighting adjustments helpsus represent our target population more closely, there is nothing to stop respondents from outside our target population to participate in our panels since it will be advertised online. To produce accurate predictions of election results, our sample needs to be acquired from a target population that will participate in the election. Therefore, it becomes necessary to include screening questions designed to filter for likely voters, based on voting history or engagement levels. Our survey includes questions that pertain to voting history, interest and engagement, voting intention, and eligibility. Responses to these questions will be used to produce an aggregate “likely voter” score that filters for the target population enabling for more accurate predictions of the presidential election.

@@

\includepdf[pages=-]{..other/datasheet/Poll Survey - Google Forms.pdf}

# Additional data details

>>>>

## Target Population and Sampling Frame
The poll targets registered voters in the United States, with a particular focus on voters in swing states for presidential races. Consequently, the target population is registered voters of the United States of America and the sampling frame is the voter file, a national list of registered voters from which NYC employs random sampling to create their pollsters [@nytpoll]. This voter file contains information on more than 200 million Americans that includes information about their party affiliation, voting history, and  basic demographic information. From this sampling frame, respondents are randomly selected while balancing key demographic and political characteristics through both front-end sampling and post-survey weighting pursuant to appropriate representation of the entire target population [@nytpoll].

@@

## Non-Response Remedies
With a response rate of 2%, there is valid concern over non-response bias underrepresenting certain demographics. The poll addresses non-response through a combination of front-end sampling adjustments (calling harder-to-reach voters) and post-survey weighting. Weighting is applied to ensure that the final sample aligns with the demographic and political composition of the electorate, based on voter file data. Non-response bias is a persistent challenge, and even though weighting helps, it's impossible to be certain that respondents are fully representative of those who do not respond. Experiments with alternative methods, such as mail surveys with incentives of cash vouchers have shown to increase response rate up to 30% [@nytpoll].

@@

The Times/Siena Poll’s approach to questionnaire design reflects a careful effort to craft unbiased, relevant, and inclusive questions. By tailoring questions to current events and topics of widespread interest, the poll aims to capture public sentiment on issues that directly affect voters' attitudes, such as economic conditions or recent political debates. This responsiveness to current events strengthens the poll's relevance and allows it to track shifts in opinion over time. The poll’s commitment to neutrality is a significant strength. Each question is designed to ensure that respondents, regardless of their political views, feel that their perspectives are fairly represented. The team behind the poll spends substantial time crafting response options to reflect a balanced spectrum of views, minimizing potential response bias and enhancing the questionnaire's reliability across different demographic and ideological groups [@nytpoll]. Clarity is also a central focus in their questionnaire development. The team emphasizes ensuring that each question is clear and unambiguous, minimizing the risk of misinterpretation. This dedication to straightforward, widely understandable questions improves the validity of responses, as it reduces the chance that respondents interpret questions differently based on background or knowledge level.

@@

Although weighting adjustments helps us represent our target population more closely, there is nothing to stop respondents from outside our target population to participate in our panels since it will be advertised online. To produce accurate predictions of election results, our sample needs to be acquired from a target population that will participate in the election. Therefore, it becomes necessary to include screening questions designed to filter for likely voters, based on voting history or engagement levels. Our survey includes questions that pertain to voting history, interest and engagement, voting intention, and eligibility. Responses to these questions will be used to produce an aggregate “likely voter” score that filters for the target population enabling for more accurate predictions of the presidential election.

@@
